---
title: "IPBES ↔ IPCC Graph Export"
output:
  html_document:
    toc: true
    toc_depth: 2
    self_contained: true
  pdf_document:
    toc: true
params:
  settings: !r list()
  graph_png: ""
  graph_nodes: !r data.frame()
  graph_edges: !r data.frame()
  edges_df: !r data.frame()
  glossary_df: !r data.frame()
  generated_at: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

## Export Metadata

- Generated at: `r params$generated_at`
- Rows in directed-edge table: `r if (is.null(params$edges_df)) 0 else nrow(params$edges_df)`
- Rows in glossary table: `r if (is.null(params$glossary_df)) 0 else nrow(params$glossary_df)`

## Current Settings

```{r settings}
settings_df <- data.frame(
  Setting = names(params$settings),
  Value = vapply(params$settings, function(x) {
    if (is.null(x)) return("")
    x <- as.character(x)
    if (!length(x)) return("")
    x[[1]]
  }, character(1)),
  stringsAsFactors = FALSE
)

knitr::kable(settings_df, format = "simple")
```

## Similarity and SS Score Explanation

### Definition similarity measures (percentages)

- `Within IPBES`: mean pairwise cosine similarity among IPBES definitions of a term.
- `Within IPCC`: mean pairwise cosine similarity among IPCC definitions of a term.
- `Between All`: mean cosine similarity across all cross pairs (`IPBES x IPCC`).

How computed:

- lowercase, punctuation removed, whitespace tokenization, stopword filtering,
  no stemming/lemmatization
- cosine similarity on token-frequency vectors

How to read:

- `100%`: identical cleaned token-frequency representation
- high: very similar wording
- mid: partial lexical overlap
- low: mostly different wording
- lexical comparison only (not a semantic/paraphrase model)

### Directed subsumption score (SS)

Graph edge score (`parent -> child`):

`score = 0.55 * lex_sub + 0.25 * def_contain + 0.20 * def_sim`

Where:

- `lex_sub`: fraction of parent term tokens found in child term tokens
- `def_contain`: fraction of parent term tokens found in child definition text
- `def_sim`: cosine similarity between combined parent/child definitions

Interpretation:

- higher SS score => stronger evidence for parent subsuming child
- raising the minimum SS threshold keeps fewer, stronger edges
- lowering the threshold includes weaker/less certain edges

## Graph Snapshot

```{r graph}
if (knitr::is_html_output()) {
  if (requireNamespace("visNetwork", quietly = TRUE) &&
      is.data.frame(params$graph_nodes) &&
      nrow(params$graph_nodes) > 0) {
    visNetwork::visNetwork(
      nodes = params$graph_nodes,
      edges = params$graph_edges,
      width = "100%",
      height = "760px"
    ) |>
      visNetwork::visHierarchicalLayout(
        direction = "UD",
        sortMethod = "directed",
        levelSeparation = 230,
        nodeSpacing = 180,
        treeSpacing = 220,
        blockShifting = FALSE,
        edgeMinimization = FALSE,
        parentCentralization = TRUE
      ) |>
      visNetwork::visNodes(
        shape = "dot",
        font = list(size = 18, face = "Segoe UI")
      ) |>
      visNetwork::visEdges(
        arrows = list(to = list(enabled = TRUE, scaleFactor = 0.5)),
        smooth = list(
          enabled = TRUE,
          type = "cubicBezier",
          forceDirection = "vertical",
          roundness = 0.16
        )
      ) |>
      visNetwork::visInteraction(
        hover = TRUE,
        navigationButtons = TRUE,
        zoomView = TRUE,
        dragView = TRUE,
        dragNodes = TRUE
      ) |>
      visNetwork::visPhysics(enabled = FALSE)
  } else {
    cat("Interactive graph was not available. Falling back to static image.\n\n")
    if (is.character(params$graph_png) && nzchar(params$graph_png) && file.exists(params$graph_png)) {
      knitr::include_graphics(params$graph_png)
    } else {
      cat("Graph image was not available during export.")
    }
  }
} else {
  if (is.character(params$graph_png) && nzchar(params$graph_png) && file.exists(params$graph_png)) {
    knitr::include_graphics(params$graph_png)
  } else {
    cat("Graph image was not available during export.")
  }
}
```

## Top Directed Edges (Selected Tree)

```{r edges}
if (is.null(params$edges_df) || nrow(params$edges_df) == 0) {
  cat("No directed edges available for the selected tree.")
} else {
  knitr::kable(params$edges_df, format = "simple")
}
```

## Glossary Table (Selected Tree)

```{r glossary}
if (is.null(params$glossary_df) || nrow(params$glossary_df) == 0) {
  cat("No glossary rows available for the selected tree.")
} else {
  knitr::kable(params$glossary_df, format = "simple")
}
```
